|

### 2021-08-20 article/article.Rmd
adding abstract, updating references

Adding more seats and more challengers further reduce the incentives to expose corrupt politicians, and the reason is twofold. First, adding more seats create free-riding incentives, as it increases the absolute number of competitors, even when the ratio of competitors-per-seat is kept constant. Second, adding more seats increase the likelihood of coordination failure, as the same incumbent may be exposed more than once while others may be not exposed at all. These two effects lower the incentives for exposing corrupt politicians, and they reasonably explain why countries with open-list proportional representation systems are endemic corrupt \citep{Myerson1993, ames1995electoral, mello2018brazil}.

@@

Electoral systems are embedded into an array of trade-offs, and also generate many other political and representational effects within the society. Majoritarian systems are great for accountability, as they foster clarity of responsibility \citep{tavits2007clarity, xezonakis2015can}, and as this paper shows, they also promote lower levels of corruption. However, they also tend to be highly polarizing and have a considerable amount of wasted votes, which grow steadily with the number of candidates credibly competing for the seat. On the other extreme, proportional representation systems ensure less wasted votes, but parties proliferate on it. It quickly becomes ungovernable without broad coalitions and inter-party agreements, which are usually rigged by corruption in developing economies \citep{mello2018brazil}.

@@

Finally, small district sizes in proportional representation, such as in the Chilean electoral system, maybe not only positive for the interplay between representation and accountability \citep{carey2011electoral}, but also in lowering corruption, when compared with large district proportional representation. The Brazilian system, with weak parties, open-list proportional representation, and large district sizes (varying between 8 and 70 legislators) proves that corruption can easily become endemic, with considerable negative impact on the quality of democracy and accountability \citep{avis2016government, mello2018brazil}.

>>>>

Adding more seats and more challengers further reduce the incentives to expose corrupt politicians, and the reason is twofold. First, adding more seats create free-riding incentives, as it increases the absolute number of competitors, even when the ratio of competitors-per-seat is kept constant. Second, adding more seats increase the likelihood of coordination failure, as the same incumbent may be exposed more than once while others may be not exposed at all. These two effects lower the incentives for exposing corrupt politicians, and they reasonably explain why countries with open-list proportional representation systems are endemic corrupt \citep{Myerson1993, ames1995electoral}.

@@

Electoral systems are embedded into an array of trade-offs, and also generate many other political and representational effects within the society. Majoritarian systems are great for accountability, as they foster clarity of responsibility \citep{tavits2007clarity, xezonakis2015can}, and as this paper shows, they also promote lower levels of corruption. However, they also tend to be highly polarizing and have a considerable amount of wasted votes, which grow steadily with the number of candidates credibly competing for the seat. On the other extreme, proportional representation systems ensure less wasted votes, but parties proliferate on it. It quickly becomes ungovernable without broad coalitions and inter-party agreements, which are usually rigged by corruption in developing economies.

@@

Finally, small district sizes in proportional representation, such as in the Chilean electoral system, maybe not only positive for the interplay between representation and accountability \citep{carey2011electoral}, but also in lowering corruption, when compared with large district proportional representation. The Brazilian system, with weak parties, open-list proportional representation, and large district sizes (varying between 8 and 70 legislators) proves that corruption can easily become endemic, with considerable negative impact on the quality of democracy and accountability \citep{avis2016government}.
